\begin{thebibliography}{9}

\bibitem{sendmail}
sendmail,
\emph{}
\url{http://www.sendmail.com/sm/open_source/}

\bibitem{postfix}
postfix,
\emph{It is Wietse Venema's mail server that started life at IBM research as an alternative to the widely-used Sendmail program.}
\url{http://www.postfix.org/}

\bibitem{exim}
exim,
\emph{Exim is a message transfer agent (MTA) developed at the University of Cambridge for use on Unix systems connected to the Internet.}
\url{http://www.exim.org/}

\bibitem{dovecot}
dovecot,
\emph{Dovecot is an open source IMAP and POP3 email server for Linux/UNIX-like systems, written with security primarily in mind. Dovecot is an excellent choice for both small and large installations. It's fast, simple to set up, requires no special administration and it uses very little memory.}
\url{http://www.dovecot.org/}

\bibitem{courier}
courier,
\emph{The Courier mail transfer agent (MTA) is an integrated mail/groupware server based on open commodity protocols, such as ESMTP, IMAP, POP3, LDAP, SSL, and HTTP. Courier provides ESMTP, IMAP, POP3, webmail, and mailing list services within a single, consistent, framework.}
\url{http://www.courier-mta.org/}

\bibitem{amavisd}
amavisd-new,
\emph{High-performance interface between mailer (MTA) and content checkers: virus scanners, and/or SpamAssassin.}
\url{http://www.ijs.si/software/amavisd/}

\bibitem{SpamAssassin}
SpamAssassin,
\emph{SpamAssassin uses a wide variety of local and network tests to identify spam signatures. This makes it harder for spammers to identify one aspect which they can craft their messages to work around.}
\url{http://spamassassin.apache.org/}

\bibitem{postgrey}
postgrey,
\emph{Postgrey is a Postfix policy server implementing greylisting developed by David Schweikert.}
\url{http://postgrey.schweikert.ch/}

\bibitem{clam-av}
clam-av,
\emph{ClamAV is an open source (GPL) antivirus engine designed for detecting Trojans, viruses, malware and other malicious threats.}
\url{http://www.clamav.net/lang/en/}

\end{thebibliography}
