\subsection{Parameter}

\paragraph{scripts}

\statement{scripts}{--scripts \typestring$|$\typefile$|$\typeurl$|$\typeuri}

Sets the location for the server scripts as a string, file, URL or URI.
A string will be interpreted according to the format. If no scheme is used the string
is assumed to be a local file, otherwise the string is assumed to be a URI.

The URI must be absolute and start with the scheme such as file: or ftp:,
followed by the file name. Some examples:
\begin{compactitem}
\item \code{--scripts file:///\\home/user/scripts.zip}
\item \code{--scripts ftp://\\exampe.com/scripts}
\end{compactitem}

The scripts can be in a directory or a container file. The container files
can be compressed files in the Bzip2, Gzip, Jar or Zip format. Multiple
scripts locations can be set. All set locations are concedered when searching
for server scripts.

\paragraph{profile}

\statement{profile}{--profile \typestring}

Sets the profile to activate. The profile name is searched in each of the
script files in each of the set scripts locations that match the regular expression:

\begin{compactitem}
\item ``\code{.+Profile\textbackslash.\textbackslash{}w+\$}''
\end{compactitem}

The loaded profile will list the services that are deployed to the server.
Each of the services are expected in it's own script file.

\paragraph{server}

\statement{server}{--server \typestring}

Sets the server where the services are deployed. The string can be a IP address
or a host name. The server is expected to run an instance of the server control
application.

Multiple server can be set with this parameter. Server and local flag can be
used together.

\paragraph{local}

\statement{local}{--local}

Flag that indicates that the services should be deployed on the local machine.
