\subsection{MaraDNS - Ubuntu 10.04}

Ubuntu 10.04 comes with MaraDNS version 1.3 in the main repository.

\subsubsection{Properties}

The values for the default properties can be found
in \reftbl{tbl:database_mysql_ubuntu_10_04_properties}.

\paragraph{install\_command}

\property{database!install\_command}{install\_command \typestring}

The command to install package on the Ubuntu system.

\paragraph{restart\_command}

\property{database!restart\_command}{restart\_command \typestring}

The restart command for the MaraDNS server.

\paragraph{mysqladmin\_command}

\property{database!mysqladmin\_command}{mysqladmin\_command \typestring}

The \command{database!mysqladmin}{mysqladmin} command.

\paragraph{mysql\_command}

\property{database!mysql\_command}{mysql\_command \typestring}

The \command{database!mysql}{mysql} command.

\paragraph{configuration\_directory}

\property{database!configuration\_directory}{configuration\_directory \typestring}

The path of the MaraDNS configuration directory.

\paragraph{mysqld\_configuration\_file}

\property{database!mysqld\_configuration\_file}{mysqld\_configuration\_file \typestring}

The file name of the {@code mysqld} configuration file.

\paragraph{packages}

\property{database!packages}{packages \typelist}

The packages needed for the MaraDNS service.

\paragraph{default\_character\_set}

\property{database!default\_character\_set}{default\_character\_set \typestring}

The default character set for databases.

\paragraph{default\_collate}

\property{database!default\_collate}{default\_collate \typestring}

The default collate for databases.
