\label{sec:postfix_profile}
\subsection{Postfix Profile}

%% storage
\TheProperty[mail:postfix:storage]{storage}
\TheProperty*[mail!postfix!storage]{storage \Arg{name}}

The \Arg{name} of the postfix storage. Can be one of the following 
storage types.
\begin{asparaitem}
%
\item[\qcode{hash}:] 
the normal postfix storage. The aliases and domains are stored in Hash files.
Supports shared domains, UNIX system accounts;
separate domains, Unix system accounts; separate domains, non-UNIX accounts.
%
\item[\qcode{postfix}:] supports the same types as the normal 
postfix storage but with MySQL as the back-end mail.
%
\end{asparaitem}

%% banner
\TheProperty[mail:postfix:mysql:banner]{banner}
\TheProperty*[mail!postfix!mysql!banner]{banner \Arg{text}}

Sets the banner \Arg{text} that follows the 220 status code in the SMTP 
greeting banner. The text can contain storage specific variables. Caution
must be taked with banner text that contains backslashes \qcode{\textbackslash} and 
dollar signs \qcode{\$}. Dollar signs may be treated as references to 
captured subsequences and backslashes are used to escape literal characters 
in the banner text.
For the distribution
\begin{inparaitem}
\item[\TheDistribution{ubuntu}] Ubuntu 10.04
\end{inparaitem}
the value is set to \qcode{\textbackslash\$myhostname ESMTP \textbackslash\$mail\_name}.

%% default_destinations
\TheProperty[mail:postfix:mysql:default_destinations]{default\_\\destinations}
\TheProperty*[mail!postfix!mysql!default\_destinations]{default\_destinations \Arg{domains}}

List of \Arg{domains} that are appended to the destinations.
Caution must be taked with the domain names that contains backslashes \qcode{\textbackslash} and 
dollar signs \qcode{\$}. Dollar signs may be treated as references to 
captured subsequences and backslashes are used to escape literal characters  in the domain name.
The value is set to \qcode{\textbackslash\$myhostname, localhost.\textbackslash\$mydomain}.

%% mailbox_base_pattern
\TheProperty[mail:postfix:mysql:mailbox_pattern]{mailbox\_pattern}
\TheProperty*[mail!postfix!mysql!mailbox\_pattern]{mailbox\_pattern \Arg{pattern}}

Sets the \Arg{pattern} for the directories that are created for each virtual
domain and virtual user under the mailbox base directory. 
Various variables can be used to specify the pattern.
Each of the variables needs to be eclosed in \qcode{\$\{\}}.
\begin{compactitem}
\item[\qcode{domain}:] the domain name of the virtual user;
\item[\qcode{user}:] the user name of the virtual user;
\end{compactitem}
Default is set the \qcode{\$\{domain\}/\$\{user\}} pattern.
